\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-27 4-other-features.Rmd
misc small fixes

The cubble workflow fits works well with an interactive graphics pipeline (e.g. @buja1988elements, @buja1996interactive,  @sutherland2000orca, @xie2014reactive, @cheng2016enabling) that is available in R with the package crosstalk [@crosstalk]. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (left). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (middle) will be selected. The long cubble will then highlight the corresponding series in the time series plot (right).

>>>>

The cubble workflow fits works well with an interactive graphics pipeline (e.g. @buja1988elements, @buja1996interactive,  @sutherland2000orca, @xie2014reactive, @cheng2016enabling) that is available in R with the package crosstalk [@crosstalk]. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (a). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (b) will be selected. The long cubble will then highlight the corresponding series in the time series plot (c).

### 2022-06-27 jss/cubble-jss.tex
misc small fixes

@@

The cubble workflow fits works well with an interactive graphics pipeline (e.g. \citet{buja1988elements}, \citet{buja1996interactive}, \citet{sutherland2000orca}, \citet{xie2014reactive}, \citet{cheng2016enabling}) that is available in R with the package crosstalk \citep{crosstalk}. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (left). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (middle) will be selected. The long cubble will then highlight the corresponding series in the time series plot (right).

@@

{\centering \includegraphics{figures/basic-manip-1}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
R> dt <- as_cubble(
+   raw, vars = c("q", "z"),
+   long_range = seq(-180, 180, 1), lat_range = seq(-90, 90, 1))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics{figures/netcdf-1}

@@

This work is funded by a Commonwealth Scientific and Industrial Research Organisation (CSIRO) Data61 Scholarship and started while Nicolas Langrené was affiliated with CSIRO's Data61. The article is created using \pkg{knitr} \citep{knitr} and \pkg{rmarkdown} \citep{rmarkdown} in R. The source code for reproducing this paper can be found at: \url{https://github.com/huizezhang-sherry/paper-cubble}.

>>>>

The \texttt{rticles::jss\_article} template used during preparation (\url{https://github.com/rstudio/rticles/tree/c085e125d874c11bb474ec53f4b754e179f8a4e9}) has the behavior that a reference prints out all the author names when it is used for the first time. See a standalone example \href{https://github.com/huizezhang-sherry/jss}{here}.

Here a hack is used to overcome this temporarily

Here I reference \citet{ctvspatiotemporal}, \citet{bach_review_2014}, \citet{lu_multidimensional_2018}, \citet{tidyverse}, \citet{tibble}, \citet{sf}, \citet{stars}, \citet{spacetime}, \citet{dplyr}, \citet{ggplot2}, \citet{tsibble}, \citet{hassell_data_2017}, \citet{tidydata}, \citet{leaflet}, \citet{crosstalk}, \citet{cheng2016enabling}, \citet{buja1996interactive}, \citet{xie2014reactive}, \citet{sutherland2000orca}, \citet{buja1988elements}, \citet{Wickham2012-yr}, \citet{hersbach2020era5}, \citet{tidync}, \citet{rnetcdf}, \citet{ncdf4}, \citet{ecwmfr}, \citet{simmons2020global}, \citet{simmons2005ecmwf}, \citet{mcintosh2018using}, \citet{stuart2010matching}, \citet{castanedo2013review}, \citet{cocchi2019data}, \citet{knitr}, \citet{rmarkdown}, \citet{wang2020calendar}, \citet{advr}, \citet{CS07Author}=``Cook, D. and Swayne, D.'',, \citet{bom}, \citet{noaa}, \citet{cds}, \citet{wickham_tourr_2011}

@@

The cubble workflow fits works well with an interactive graphics pipeline (e.g. \citet{buja1988elements}, \citet{buja1996interactive}, \citet{sutherland2000orca}, \citet{xie2014reactive}, \citet{cheng2016enabling}) that is available in R with the package crosstalk \citep{crosstalk}. Figure \ref{fig:illu-interactive} illustrates how linking can be achieved between a map and multiple time series using a cubble. The map (produced from the nested form) and time series (produced from the long form) are both shared crosstalk objects. When a user makes a selection on the map, the site is highlighted (a). This activates a row in the nested cubble object, which is then communicated to the long cubble -- all the observations with the same \code{id} (b) will be selected. The long cubble will then highlight the corresponding series in the time series plot (c).

@@

{\centering \includegraphics[width=1\linewidth]{figures/basic-manip-1}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
R> dt <- as_cubble(
+   raw, vars = c("q", "z"),
+   long_range = seq(-180, 180, 1), lat_range = seq(-88, 88, 1))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{figures/netcdf-1}

@@

This work is funded by a Commonwealth Scientific and Industrial Research Organisation (CSIRO) Data61 Scholarship and started while Nicolas Langrené was affiliated with CSIRO's Data61. The article is created using \pkg{knitr} \citep{knitr} and \pkg{rmarkdown} \citep{rmarkdown} in R using the \texttt{rticles::jss\_article} template. The source code for reproducing this paper can be found at: \url{https://github.com/huizezhang-sherry/paper-cubble}.
